\section{Conclusion}
\label{sec:conclusion}

We studied task-state monitoring in firefighter incident command as a bounded coordination-support capability for an incident-command dashboard.

The central system-design question was whether this capability depends on speaker identities and explicit utterance boundaries, both of which can be expensive or difficult to obtain robustly from radio communication. For the controlled setting studied here, the answer is largely no: reduced transcript structure does not materially change the overall task-monitoring performance profile. The main remaining weaknesses are unit-related assignment timing in incremental prefixes and capturing the reported completion result rather than detecting assignment or completion itself, and both remain broadly similar across transcript conditions.

More broadly, this suggests that some coordination-support functions may be feasible without heavy transcript preprocessing. Methodologically, the paper also shows how a source-grounded synthetic dataset construction and validation pipeline can support controlled comparison of transcript-structure conditions while holding operational content fixed. At the same time, the present evidence remains deliberately narrow: it comes from a controlled synthetic dataset, from text rather than raw audio, and from a closed-world monitoring task. Future work should therefore test whether the same pattern holds under noisier audio pipelines, less linear communication, and stronger ambiguity, while improving unit-assignment grounding, evidence presentation, and human-in-the-loop integration into command workflows. A further direction is to move from closed-world monitoring toward mixed closed- and open-world coordination support, where systems track predefined tasks while also identifying additional operational tasks that emerge from the incident record. Another direction is to connect evolving coordination state to relevant supporting knowledge resources, so that a shared dashboard can surface applicable procedures, plans, or reference documents without turning the system into an autonomous decision maker.
