\documentclass[11pt]{article}

% Change "review" to "final" to generate the final (sometimes called camera-ready) version.
% Change to "preprint" to generate a non-anonymous version with page numbers.
\usepackage[review]{acl}

% Standard package includes
\usepackage{times}
\usepackage{latexsym}

% For proper rendering and hyphenation of words containing Latin characters (including in bib files)
\usepackage[T1]{fontenc}
% For Vietnamese characters
% \usepackage[T5]{fontenc}
% See https://www.latex-project.org/help/documentation/encguide.pdf for other character sets

% This assumes your files are encoded as UTF8
\usepackage[utf8]{inputenc}

% This is not strictly necessary, and may be commented out,
% but it will improve the layout of the manuscript,
% and will typically save some space.
\usepackage{microtype}

% This is also not strictly necessary, and may be commented out.
% However, it will improve the aesthetics of text in
% the typewriter font.
\usepackage{inconsolata}

%Including images in your LaTeX document requires adding
%additional package(s)
\usepackage{graphicx}
\usepackage{booktabs}

% If the title and author information does not fit in the area allocated, uncomment the following
%
%\setlength\titlebox{<dim>}
%
% and set <dim> to something 5cm or larger.

\title{A Bounded Coordination-Support Capability for Multi-Party Settings: Task-State Monitoring in Firefighter Incident Command}

% Author information
\author{David Grünert \and Barbara Morgenstern \and Florian Peczinka \\
\textbf{\and Dario Holenstein \and Roland Brunner \and Alexandre de Spindler} \\
Zurich University of Applied Sciences, Winterthur, Switzerland \\
\texttt{\{grud,morgebar,pecziflo,holendar,desa\}@zhaw.ch} \\
Freiwillige Feuerwehr Stadt Zug, Zug, Switzerland \\
\texttt{roland.brunner@stadtzug.ch}}


\begin{document}
\maketitle
\begin{abstract}
  Many coordination settings require digital support systems for several humans who coordinate through shared state and ongoing communication. We study one such application in firefighter incident command: a dashboard that monitors the state of predefined operational tasks from radio transcripts.
  Building such a dashboard raises a practical design question: how much transcript structure is actually needed for LLM-based task-state monitoring? Rich transcript structure may require speaker diarization, speaker-change detection, or semantically refined utterance segmentation, all of which are difficult to obtain reliably from radio communication and can add complexity and latency.
  We evaluate this question on source-grounded synthetic firefighter scenarios under transcript conditions that vary speaker identity and utterance boundaries, with incremental inference as the deployment-facing condition and full-transcript inference as an offline reference.
  Across repeated runs, incremental monitoring remains strong across all transcript conditions. Differences between transcript structures are small, continuous transcripts remain competitive, and the main weaknesses are identifying the responsible unit and capturing the completion result, which remain broadly similar across conditions.
  These results suggest that for this bounded dashboard-support capability, neither speaker identities nor semantically precise utterance boundaries are a primary requirement in the controlled setting studied here.
\end{abstract}

\input{introduction}
\input{background}
\input{application}
\input{dataset}
\input{experimental_setup}
\input{evaluation}
\input{conclusion}
\clearpage

% Custom bibliography entries only
\bibliography{bibliography}

\end{document}
